---
title             : "A Diverse Happiness for a Diversifing World: The Relationship between Community-level Racial Diversity and Psycholoigcal Richness"
shorttitle        : "A Diverse Happiness for a Diversifing World"

author: 
  - name          : "Brett Neely Peterson"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "bnpeterson@uchicago.edu"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"
    role:
      - "Writing - Review & Editing"
      - "Supervision"

affiliation:
  - id            : "1"
    institution   : "The University of Chicagi"
  - id            : "2"
    institution   : "Konstanz Business School"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  One or two sentences to put the results into a more **general context**.
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : "new-r-references.bib"

floatsintext      : no
linenumbers       : yes
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
library(tidyverse)
library(psych)
library(stats)
library(lme4)
library(scales)
library(jtools)
library(broom)
library(tidyverse)
library(ggplot2)
library(readr)
r_refs("new-r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Literature Review


## A Diversifying World
Increasing levels of diversity have become hallmarks of the modern, globalizing world. With greater global inter-connectivity, the expanded communication tools, technological development, and the increased global migration, many people now have greater opportunities to interact with people different from themselves racially, religious, or culturally than perhaps at any other point in history. This increasing diversification presents both profound possibilities and potential challenges as people grapple with the changing social and communal dynamics. Therefore, in light of both this increasing diversification and the often mixed responses to it, it is especially valuable now to understand how living within a diverse community impacts individual well-being. However, the relationship between diversity and psychological richness, a vital component of human well-being, has largely gone unexplored up to this point. Therefore, this paper will seek to address this question of how living within a racially diverse community affects individual levels of psychological richness through a series of studies in this area. In order to address this question, this paper proposes a two primary hypotheses regarding the relationship between the degree of diversity in one’s community and the prevalence of psychological richness:

> *H1: Living within an ethnically diverse or heterogeneous community leads people to have greater degrees of psychological richness.*

> *H2: This change in psychological richness is at least partially explained by a more racially diverse social networks exposing individuals to different perspectives and experiences.*

In order to address this central question regarding diversity and psychological richness along with these corresponding hypotheses, however, one must first examine the current relevant literature regarding diversity, well-being, and psychological richness so that a clear link between these concepts can be established.

## Constrict Theory: A Direct Challenge to Well-being
First, understanding the impact of diversity on the different members within a community is vital for understanding how it might impact individual well-being. In his landmark research findings on diversity, 
@putnamPluribusUnumDiversity2007 finally addressed the on-going debate between the contact and conflict theories of diversity by presenting extensive data supporting a new model, known as the “constrict theory” of social capital (p. 144). Rather than either decreasing racial animosity [@allportNaturePrejudiceGordon1954; @brownChildhoodCrossethnicExposure2021; @duboisPhiladelphiaNegroSocial1899; @sigelmanContactHypothesisRevisited1993; @stoufferAmericanSoldierAdjustment1949] or increasing a sense of outgroup threat [@enosCausalEffectIntergroup2014; @enosWhatDemolitionPublic2016; @gilesPowerApproachIntergroup1986; @herbertblumerRacePrejudiceSense1958], Putnam found that diversity actually has this “constricting” effect where increasing diversity actually lowers trust for both in-group and out-group communities which leads to greater social isolation and overall weaker social capital [@putnamPluribusUnumDiversity2007, p. 144, 149-150]. Based on Putnam’s research regarding the constrict theory, therefore, one could reasonably assume that greater diversity may lead to lower overall well-being since happiness and meaning, two of the primary factors in well-being, are both connected to social support and connecting to something greater than one’s self [@oishiPsychologicallyRichLife2022, p. 791-792]. In fact, @sederEthnicRacialHomogeneity2009 actually found this type of diversity effect when conducting research that demonstrated university students with more homogenous friendship networks on Facebook actually scored higher on life satisfaction and positive feelings than those with more heterogenous networks (p. 443). Similar results were also found both by @florezUnderstandingMeaningRacial2019 who demonstrated that higher levels of meaning are associated with higher degrees of prejudice and by @elnakouriHateMeaningLife2022 [, p. 5] who demonstrated that collective hate towards a group, as opposed to individual hate towards a specific person often produced higher meaning in life. Therefore, based on the preponderance of the current research on diversity and its impact on well-being, one might reasonably assume that living within a diverse community would reduce overall well-being. 

## A Potential Answer: Psychological Richness
While portions of the current literature may appear to present a negative view of diversity at first glance, however, there are also substantive reasons to believe that this may not be the full picture. The current literature on diversity does convincingly demonstrate that increased diversity likely reduces happiness and meaning in certain circumstances, but these are not the only two factors that contribute to well-being. Oishi and Westgate provide compelling evidence that the current framework of human well-being should be expanded beyond happiness and meaning, to also include psychological richness, a third vital and distinct element of living a good life [@oishiPsychologicallyRichLife2022, p. 790]. While happiness is associated with stability and satisfaction, and meaning with a greater purpose, psychological richness on the other hand is defined by a sense of experiencing perspective-changing exploration that contributes to living a good life [@oishiPsychologicallyRichLife2022, p. 790]. In this manner, psychological richness is often associated with an openness to new experiences, an awareness that one’s perspective is not definitive or universal, a higher penchant for creativity and narrative complexity, and also a willingness to consider challenging experiences rewarding even if difficult [@oishiPsychologicallyRichLife2022, p. 790, 794, 797-798, 804]. Because of these different causes and features, it is possible that psychological richness may have a different relationship with diversity than either happiness or meaning. Therefore, since past studies have only focused on the relationship between diversity and these first two components of well-being, it also remains possible that the current literature on diversity has unintentionally presented an overly negative portrayal of diversity by not considering how it may impact psychological richness as well. 

Additionally, there are reasons to believe that psychological richness, unlike happiness and meaning, is positively correlated with diversity based on the current literature. First, political liberalism, a factor commonly associated with racial openness, is instead highly related to psychological richness [@oishiExperiencesAssociatedPsychological2021, p. 755]. Second, psychological richness has proven to be more resistant to challenges and traumatic events than either happiness or meaning, so it is possible that the different challenges inherent in increasing diversity may not affect psychological richness in the same way as its counterparts [@oishiPsychologicallyRichLife2022, p. 804-804]. Finally, while a link between diversity and psychological richness has yet to be definitively proven, the current research has demonstrated that certain experiences which involve increased exposure to diversity, such as studying abroad, do in fact increase rates of psychological richness while not having a similar impact on happiness or meaning @oishiPsychologicallyRichLife2022, p. 797]. Based on the substantive evidence of the current literature on psychological richness, therefore, there are substantial reasons to believe that psychological richness, unlike happiness and meaning, may actually have a positive causal relationship with increased racial diversity. 


# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure


```{r loading_data}

Zipcode_data_with_Regions_States <- read_csv("~/repos/Diversity-Richness/Zip.Code.Datasets/Zipcode_data_with_Areas_States.csv")

```

```{r race-median-income-fig, fig.cap="ZIP Code Median Household Income by Percentage of the Poluation of Each Demgraphic"}

ggplot(Zipcode_data_with_Regions_States) +
  geom_smooth(aes(x = X_Total_Population_White_Alone, y = Median_Household_Income, color = "#A1C9F4"), fill ="grey", alpha = 0.2, show.legend = T)  +
  geom_smooth(aes(x = X_Total_Population_Black_or_African_American_Alone, y = Median_Household_Income, color = "#FFB482"), fill = "grey", alpha = 0.2, show.legend = T) + #Fixed shading
  geom_smooth(aes(x = X_Total_Population_Asian_Alone, y = Median_Household_Income, color = "#8DE5A1"), fill = "grey", alpha = 0.2, show.legend = T) +
  geom_smooth(aes(x = X_Total_Population_American_Indian_And_Native_Alaskan_Alone, y = Median_Household_Income, color = "#D0BBFF"), fill = "grey", alpha = 0.2, show.legend = T) +
  geom_smooth(aes(x = X_Hispanic, y = Median_Household_Income, color = "#FF9F9B"), fill = "grey", alpha = 0.2, show.legend = T) +
  scale_color_manual(values = c( "#8DE5A1" = "#8DE5A1","#A1C9F4" = "#A1C9F4","#D0BBFF" = "#D0BBFF", "#FF9F9B" = "#FF9F9B", "#FFB482" = "#FFB482"), #Fixed order
                     name = "Race",
                     labels = c("Asian", "White", "Native American/Alaskan", "Hispanic", "Black")) +
  labs(x = "Percentage Population of Population for Each Racial Demgraphic", y = "Median Household Income", title = "Racial Demographics and Median Household Income")
```


This is to check whether I can finally reference Figure \@ref(fig:race-median-income-fig)

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

# Discussion


\newpage

# References

::: {#refs custom-style="Bibliography"}
:::
