---
title             : "Exploring RStudio"
shorttitle        : "Explore R"

author: 
  - name          : "Brett Neely Peterson"
    affiliation   : "The University of Chicago"
    corresponding : yes    # Define only one corresponding author
    address       : "Chicago, IL"
    email         : "bnpeterson@uchicago.edu"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"

affiliation:
  - id            : "1"
    institution   : "The University of Chicago"


authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  One or two sentences to put the results into a more **general context**.
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : "r-references.bib"

floatsintext      : no
linenumbers       : yes
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : papaja::apa6_pdf
---

# 1. Loading Functions and scripts
<!-- This is the first of the three headers. -->

```{r}
source("~/repos/Diversity-Richness/Initial_Script.R") #accessing script

```

```{r}
source("~/repos/Diversity-Richness/Function_scripts.R")
# load newscript that includes scripts for helloworld
```

```{r}
#practice using the helloworld function
name <- "Dr. Dowling" #sample name
title <- TRUE #sample title
month_num <- 3 #sample month
military_time <- 15
helloworld(name, title, month_num) #sample function

```

```{r Read-in Basic Census Data}
library(readr)
reloading_censusdata <- "~/Desktop/CensusData/Census_Citydata_nolables.csv" #making a pathway to the downloaded census data
downloaded_censusdata <- read.csv(reloading_censusdata) #loading the census data with readr
View(downloaded_censusdata)
# This data is mostly in a tidy format. Each column is a single variable (although total pop is repeated several times) and each row is a single observation. Each cell is mostly a single measurement, but many are left blank including whole rows. 
# The data has issues: 1) whole rows left blank 2) repeated columns 3) difficult to use column names

```

```{r Editting Data with dyplr}
library(dplyr)
updated_census_data <- select(downloaded_censusdata, 2, 52, 60:137) #remove unneccesary coumns
updated_census_data2 <- rename(updated_census_data, "Qualifying_Name" = 1, "Area_Name" = 2, "Total_Population" = 3, "Total_Population_Male" = 4, "Total_Population_Female" = 5, "X_Total_Population_Male" =6, "X_Total_Population_Female" = 7, "Total_Population2" = 8, "Total_Population_Under_5_Years" = 9, "Total_Population_5_to_9_Years" = 10, "Total_Population_10_to_14_Years" = 11, "Total_Population_15_to_17_Years" = 12, "Total_Population_18_to_24_Years" = 13, "Total_Population_25_to_34_Years" = 14, "Total_Population_35_to_44_Years" = 15, "Total_Population_45_to_54_Years" = 16, "Total_Population_55_to_64_Years" = 17, "Total_Population_65_to_74_Years" = 18, "Total_Population_75_to_84_Years" = 19, "Total_Population_85_Years_And_Over" = 20,"X_Total_Population_Under_5_Years" = 21, "X_Total_Population_5_to_9_Years" = 22, "X_Total_Population_10_to_14_Years" = 23, "X_Total_Population_15_to_17_Years" = 24, "X_Total_Population_18_to_24_Years" = 25, "X_Total_Population_25_to_34_Years" = 26, "X_Total_Population_35_to_44_Years" = 27, "X_Total_Population_45_to_54_Years" = 28, "X_Total_Population_55_to_64_Years" = 29, "X_Total_Population_65_to_74_Years" = 30, "X_Total_Population_75_to_84_Years" = 31, "X_Total_Population_85_Years_And_Over" = 32, "Total_Population3" = 33, "Total_Population_White_Alone" = 34, "Total_Population_Black_or African_American_Alone" = 35, "Total_Population_American_Indian_And_Native_Alaskan_Alone" = 36, "Total_Population_Asian_Alone" = 37, "Total_Population_Native_Hawaiian_And_Other_Pacific_Islander_Alone" = 38, "Total_Population_Some_Other_Race_Alone" = 39,"Total_Population_Two_Or_More_Races" = 40,"X_Total_Population_White_Alone" =41, "X_Total_Population_Black_or African_American_Alone" = 42, "X_Total_Population_American_Indian_And_Native_Alaskan_Alone" = 43, "X_Total_Population_Asian_Alone" = 44, "X_Total_Population_Native_Hawaiian_And_Other_Pacific_Islander_Alone" = 45, "X_Total_Population_Some_Other_Race_Alone" = 46,"X_Total_Population_Two_Or_More_Races" = 47,"Households" = 48,"Households_Family_Households" = 49,"Households_Married_Couple_Family" = 50,"Households_Other_Family" = 51,"Households_Male_Householder_No_Wife_Present" = 52,"Households_Female_Householder_No_Husband_Present" = 53,"Households_Nonfamily_Households" = 54,"Nonfamily_Households_Male_Householder" = 55,"Nonfamily_Households_Female_Householder" = 56,"X_Households_Family_Households" = 57,"X_Households_Married_Couple_Family" = 58,"X_Households_Other_Family" = 59,"X_Households_Male_Householder_No_Wife_Present" = 60,"X_Households_Female_Householder_No_Husband_Present" = 61,"X_Households_Nonfamily_Households" = 62,"X_Nonfamily_Households_Male_Householder" = 63,"X_Nonfamily_Households_Female_Householder" = 64,"Median_Household_Income" = 65,"Housing_Units" = 66,"Occupied_Housing_Units" = 67,"Owner_Occupied" = 68,"Renter_Occupied" = 69,"X_Owner_Occupied" = 70,"X_Renter_Occupied" = 71,"Population_With_Poverty_Status" = 72,"Poverty_Status_Under_1.00" = 73,"Poverty_Status_1.00_to_1.99" = 74,"Poverty_Status_Under_2.00" = 75,"Poverty_Status_2.00_and_Over" = 76,"X_Poverty_Status_Under_1.00" = 77,"X_Poverty_Status_1.00_to_1.99" = 78,"X_Poverty_Status_Under_2.00" = 79,"X_Poverty_Status_2.00_and_Over" = 80)
#renaming old columns
OnlyLarge_City_Data <- filter(updated_census_data2, Total_Population >= 50000)
#limiting the data to only include cities over 50000 population
```

```{r Read-out new Large City Data Set}
write.csv(OnlyLarge_City_Data, file = "~/repos/Diversity-Richness/City_Census_Over50000", row.names = FALSE)
#make a new csv file to include only the larger cities

```

```{r}
library(writexl)
write_xlsx(updated_census_data2, "~/repos/Diversity-Richness/City_Census_data_excel")
```




# 2. Research Analysis

<!-- These are the two lists. -->

**Potenial Locations**
- *City Level data*
  - Chicago 
  - Dallas
- *County Level Data*
  - Cook
  -Dallas
- *Zip Code Level Data*
  - 60637
  - 76116 

**Experiment Approaches**
1. *Experiment*
  1.1 250 particapnts 
  1.2 race of friend network
2. *City Analysis*
  2.1 50 cities
  2.2 psych richness survey
3. *Proxy Data*
  3.1 World Values Survey
  3.2 10 years 

[Link to Social Explorer](https://www.socialexplorer.com/explore-maps)
<!-- This is the link for the Census Burea Data -->


# 3. Preloaded Info

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")


```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```


```{r}


helloworld <- function(name, title, month_num) {
  formality <- if (title == TRUE) {formality <- "Greetings "
  } else {formality <- "Hey "}
  for (month_num in 1:2) {season <- "Winter"}
  for (month_num in 12) {season <- "Winter"}
  for (month_num in 3:5) {season <- "Spring"}
  for (month_num in 6:8) {season <- "Summer"}
  for (month_num in 9:11) {season <- "Fall"}
  paste0(formality, name, ", how are you? ", "I hope you are having a lovely ", season, "!")
}



```



# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

# Discussion


\newpage

# References

::: {#refs custom-style="Bibliography"}
:::
